ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
fixed odgi layout and draw
added hot sorting algorithm name

    \topic{odgi viz, sort, draw \& layout} pangenome visualization
    provides convenient insight into genomic variation (see
    Fig.~\ref{fig:1}). \cmd{odgi viz} generates a linearized
    representation of the pangenome and is capable of handling full
    length human chromosomes (Fig.~\ref{fig:1}a).  \cmd{odgi sort}
    reorganises node order and simplifies the graph by applying
    several algorithms, including the novel `NAME the
    algorithm'. \cmd{odgi layout \& draw} bring out the consensus
    graph (Fig.~\ref{fig:1}b).

>>>>

    \topic{odgi viz, sort, draw \& layout} pangenome visualization
    provides convenient insight into genomic variation (see
    Fig.~\ref{fig:1}). \cmd{odgi viz} generates a linearized
    representation of the pangenome and is capable of handling full
    length human chromosomes (Fig.~\ref{fig:1}a). \cmd{odgi sort}
    reorganises node order and simplifies the graph by applying
    several algorithms, including the novel `Path-Guided Stochastic Gradient Descent`
    algorithm. \cmd{odgi layout} and \cmd{odgi draw} bring the
    visualization in 2D. (Fig.~\ref{fig:1}b).
